### 2012-12-04 inst/examples/policycosts/costfree.Rmd
cleanup

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="writeup/")
```

``` {r}
price = 10
c0 = 30
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
c2 <- exp(seq(0, log(21), length.out = 20))-1
```

>>>>

```{r cache-options, include=FALSE}
opts_chunk$set(cache=TRUE, cache.path="costfree/")
```

``` {r}
price = 10
c0 = 0
profit <- profit_harvest(price = price, c0 = c0, c1 = 0)
c2 <- exp(seq(0, log(21), length.out = 20))-1
```
